prolfqua (prodea) - An R-package for Proteomics Differential Expression Analysis.

### 2022-04-06 inst/MyArticle/paper.Rmd
Format tables

```{r prolfquaModels}
xM <- data.frame( 
    lm = c("lm", "linear model on peptide or protein abundances", "strategy_lm, build_models, Contrasts"),
    lmer = c("lmer" , "mixed effect models on peptide and protein abundances", "strategy_lmer, build,models, Contrasts"),
    gmi = c("group mean imputation", "impute missing group means", "ContrastsSimpleImpute"),
    ROPECA = c("ROPECA","linear models on peptide abundances", "strategy_lm, build_models, Contrast, ContrastsROPECA"),
    limma = c("limma" , "empirical Bayes variance shrinkage", "ContrastsModerated"),
    pic = c("Protein interaction scoring", "by wrapping SAINT express binaries", "runSaint, ContrastsSaintExpress"),
    prodA = c("dropout model", "by warpping proDA functionality", "strategy_proDA, build_models, ContrastsProDa"), check.names =  FALSE)
xM <- data.frame(t(xM))
colnames(xM) <- c("m", "model", "prolfqua functions")
knitr::kable(xM[,2:3], caption = "Models available in prolfqua.")

@@

|       |                                                   |
|:------|:--------------------------------------------------|
|AUC    |Area Under the Curve                               |
|CDF    |Cumulative Distribution Function                   |
|ESI-MS |Electro-Spray-Ionization Mass Spectrometry         |
|FC     |Fold Change                                        |
|$FDP$  |False Discovery Proportion                         |
|$FDR$  |False Discovery Rate                               |
|HPLC   |High-Pressure Liquid Chromatography                |
|LC-MS  |Liquid Chromatography followed by Mass Spectrometry|
|LFQ    |Label-Free Quantification                          |
|LOD    |Limit Of Detection                                 |
|MS     |mass spectrometry                                  |
|OO     |Object-Oriented                                    |
|UML    |Unified Modeling Language                          |

>>>>

```{r prolfquaModels}
xM <- data.frame( 
    lm = c("lm", "linear model on peptide or protein abundances", "strategy_lm, build_models, Contrasts"),
    lmer = c("lmer" , "mixed effect models on peptide and protein abundances", "strategy_lmer, build,models, Contrasts"),
    gmi = c("group mean imputation", "impute missing group means", "ContrastsSimpleImpute"),
    ROPECA = c("ROPECA","linear models on peptide abundances", "strategy_lm, build_models, Contrast, ContrastsROPECA"),
    limma = c("limma" , "empirical Bayes variance shrinkage", "ContrastsModerated"),
    pic = c("Protein interaction scoring", "by wrapping SAINT express binaries", "runSaint, ContrastsSaintExpress"),
    prodA = c("dropout model", "by warpping proDA functionality", "strategy_proDA, build_models, ContrastsProDa"), check.names =  FALSE)
xM <- data.frame(t(xM))
colnames(xM) <- c("m", "model", "prolfqua functions")
knitr::kable(xM[,2:3], caption = "Models available in prolfqua.",
             format = "latex", booktabs=TRUE) |>
    kableExtra::kable_styling(latex_options="scale_down")
```

@@

\begin{table}[H]
\centering
\begin{tabular}[H]{ll}
\toprule
Abbreviations & Explaination\\
\midrule
AUC    &Area Under the Curve                               \\
CDF    &Cumulative Distribution Function                   \\
ESI-MS &Electro-Spray-Ionization Mass Spectrometry         \\
FC     &Fold Change                                        \\
$FDP$  &False Discovery Proportion                         \\
$FDR$  &False Discovery Rate                               \\
HPLC   &High-Pressure Liquid Chromatography                \\
LC-MS  &Liquid Chromatography followed by Mass Spectrometry\\
LFQ    &Label-Free Quantification                          \\
LOD    &Limit Of Detection                                 \\
MS     &mass spectrometry                                  \\
OO     &Object-Oriented                                    \\
UML     &       Unified Modeling Language                  \\
\bottomrule
\end{tabular}
\end{table}
